Painting with Triangles

### 2014-06-06 paper.tex
Figure rearrangement.
foo

Work has also been done in multi-resolution painting using raster graphics. \modified{Early work with Pad++ by Bederson and Hollan~\shortcite{Bederson:1994:PZG:192426.192435} 
explored the possibility of having an infinite resolution canvas. However, rather than a general painting program 
this work is focused on creating an interface builder for developers.}
The method of Berman~\etal~\shortcite{Berman:1994:MPC:192161.192181}
stores image information in a quadtree so that different parts of the image can have different levels of detail.
This means the image effectively has an infinite level of detail, yet since it is stored in raster form
there are still limitations. For example a stroke painted at coarse detail will still look blurry when
zoomed in. The strokes are limited to the resolution they are painted at. Similarly the method of Carr and Hart~\shortcite{Carr:2004:PD:1186562.1015809}
also allows the development of multi-resolution images using rasters, and as such suffers from the
same limitations. \modified{One way to reduce blurriness in raster images of sharp features is proposed by Ramanarayanan~\etal~\shortcite{ramanarayanan2004feature}. 
By seprately storing where important boundaries are, their system can avoid excessive interpolation. However, such a method requires
creating such a data structure with those stored boundaries.} Another multi-resolution approach by Perlin and Velho~\shortcite{Perlin:1995:LPP:218380.218437} uses
procedural textures to avoid any fundamental limit on resolution. Although useful,
generating procedural textures can be difficult for artists.

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. \modified{This significantly exceeds the limits
imposed by existing vector graphics software such as Adobe Illustrator, which has a maximum zoom ratio
of 64:1.  Furthermore, our ability to make paint strokes of smooth gradients in a flat vector representation (see Figure~\ref{fig:teaser}) is unique.}

>>>>

Work has also been done in multi-resolution painting using raster graphics. \modified{Early work with Pad++ by Bederson and Hollan~\shortcite{Bederson:1994:PZG:192426.192435} 
explored the possibility of having an infinite resolution canvas. However, rather than a painting program, 
this work focused on creating an interface builder for developers.}
The method of Berman~\etal~\shortcite{Berman:1994:MPC:192161.192181}
stores image information in a quadtree so that different parts of the image can have different levels of detail.
This means the image effectively has an infinite level of detail, yet since it is stored in raster form
there are still limitations. For example a stroke painted at coarse detail will still look blurry when
zoomed in. The strokes are limited to the resolution they are painted at. Similarly the method of Carr and Hart~\shortcite{Carr:2004:PD:1186562.1015809}
also allows the development of multi-resolution images using rasters, and as such suffers from the
same limitations. \modified{One way to reduce blurriness in raster images of sharp features is proposed by Ramanarayanan~\etal~\shortcite{ramanarayanan2004feature}. 
By seprately storing where important boundaries are, their system can avoid excessive interpolation. However, such a method requires
creating such a data structure with those stored boundaries.} Another multi-resolution approach by Perlin and Velho~\shortcite{Perlin:1995:LPP:218380.218437} uses
procedural textures to avoid any fundamental limit on resolution. Although useful,
generating procedural textures can be difficult for artists.

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. 
\modified{Nevertheless, this range far exceeds limits
imposed by existing vector graphics software such as Adobe Illustrator, which has a maximum zoom ratio
of 64:1.  Furthermore, our ability to make paint strokes of smooth gradients in a flat vector representation (\eg, Figure~\ref{fig:teaser}) is unique.}
